Estimating individual subjective values of emotion regulation strategies

### 2022-06-08 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
knitted document

In the original study by Westbrook et al.\textsuperscript{29}, cognitive load was varied using the \emph{n}-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
Participants had to decide in an iterative procedure whether they wanted to repeat a higher \emph{n}-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption that the objectively easiest \emph{n}-back level has the highest SV.
In the present study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest \emph{n}-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies\textsuperscript{22}.
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which precedes the other steps and where the ER option with the higher subjective value is determined.
In this step, the same monetary value (i.e., 1 €) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al.\textsuperscript{29} until the indifference point is reached.
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \ref{fig:ResponsePatterns}).
In a separate study, we will test our adapted paradigm together with a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna et al.\textsuperscript{31}).

@@

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study\textsuperscript{32}.
The paradigm was written and presented using \emph{PsychoPy}\textsuperscript{33}.
We used \emph{R} with \emph{R Studio}\textsuperscript{34,35} with the main packages \emph{afex}\textsuperscript{36} and \emph{BayesFactor}\textsuperscript{37} for all analyses.
The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at \url{https://github.com/ChScheffel/CERED}.
A complete list of all measures assessed in the study can be found at OSF (\url{https://osf.io/vnj8x/}) and GitHub (\url{https://github.com/ChScheffel/CERED}).

@@

Young healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{38} at the Technische Universität Dresden.
Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
Participants will be invited to complete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consists of two lab sessions, which will take place in a shielded cabin with constant lighting.
Before each session, participants will receive information about the respective experimental procedure and provide informed consent.
In the first session participants will fill out a demographic questionnaire and complete an n-back task with the levels one to four.
Then, they will complete an effort discounting (ED) procedure regarding the n-back levels on screen, followed by a random repetition of one n-back level.
The second session will take place exactly one week after session one.
Participants will provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
A brief training will ensure that all participants are able to implement the ER strategies.
Next, electrodes to measure facial EMG will be attached and the ER paradigm will be conducted, followed by an ED procedure regarding the ER strategies.
After that, participants will choose one ER strategy to repeat one more time.
Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden\textsuperscript{39,40}.

@@

The online survey will contain a number of questionnaires.
In the focus of the current project is the Flexible Emotion Regulation Scale (FlexER)\textsuperscript{41}.\\
It assess flexible use of ER strategies with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which we define as ER flexibility.
The items are rated on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.

Further psychological constructs will be assessed but have no clear hypothesies in the present work an are therefore investigated only exploratory:
General psychological well-being will be assessed using the German version of the WHO-5 scale\textsuperscript{42,43}.
To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{46} will be used.
Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,47}.
Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from Bernecker and Job\textsuperscript{48}.
To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{28,49} will be used.
To assess self-control,\textsuperscript{50} sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS)\textsuperscript{51}, the Brief Self-Control Scale (BSCS)\textsuperscript{52,53}, and the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{54,55}.
Attentional control will be assessed using the Attentional Control Scale (ACS)\textsuperscript{56}.
For more detailed information on psychometric properties of the questionnaires, please see \protect\hyperlink{SupplementQuestionnaires}{supplementary material}.

@@

\emph{Part one: ER task.} Part one will be a standard ER task in a block design (see Figure \ref{fig:DesignERED}), similar to paradigms previously used by our group\textsuperscript{22}.
Participants will be told to actively view neutral and negative pictures (see \protect\hyperlink{ux5cux23stimuli}{2.3.3}) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
Every participant first will have the condition ``active viewing-neutral'' that serves as a baseline condition.
During this block, 20 neutral pictures will be presented.
Participants will be asked to ``actively view all pictures and permit all emotions that may arise.''
In the second block, participants will actively view negative pictures.
During the third, fourth, and fifth block, participants will see negative pictures and will be asked to regulate their emotions using distraction, distancing, and suppression.
In order to achieve distraction, participants will be asked to think of a geometric object or an everyday activity, like brushing their teeth.
During distancing, participants will be asked to ``take the position of a non-involved observer, thinking about the picture in a neutral way.''
Participants will be told not to re-interpret the situation or attaching a different meaning to the situation.
During suppression, participants will be told to ``suppress their emotional facial expression.''
They should imagine being observed by a third person that should not be able to tell by looking at the facial expression whether the person is looking at an emotional picture.
Participants will be instructed not to suppress their thoughts or change their facial expression to the opposite\textsuperscript{22}.
All participants will receive written instruction and complete a training session.
After the training session, participants will be asked about their applied ER strategies to avoid misapplication.
The order of the three regulation blocks (distraction, distancing, and suppression) will be randomized between participants.
Each of the blocks consisted of 20 trials showing neutral (Block 1) and negative (Blocks 2, 3, 4, 5) pictures.
Each trial began with a fixation cross that lasted 3 to 5 seconds (random uniform distributed).
It was followed by neutral or negative picture for a total of 6 seconds.
After each block, participants retrospectively rated their subjective emotional arousal (``not at all aroused'' to ``very highly aroused''), their subjective effort (``not very exhausting'' to ``very exhausting''), and - after the ragulation blocks - the utility of the respective strategy (``not useful at all'' to ``very useful'') on a continuous scale using a slider on screen.

@@

Pictures that will be used in the paradigm are selected from the Emotional Picture Set (EmoPicS)\textsuperscript{57} and the International Affective Picture System (IAPS)\textsuperscript{58}.
The 20 neutral pictures (Valence (V): \emph{M} \(\pm\) \emph{SD} = 4.81 \(\pm\) 0.51; Arousal (A): \emph{M} \(\pm\) \emph{SD} = 3 \(\pm\) 0.65) depicted content related to the categories persons, objects, and scenes.
Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, will be used.
An evolutionary algorithm\textsuperscript{59} is used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
A complete list of all pictures and their classification into sets can be found in supplementary material 1.
The five sets of negative pictures will be assigned randomly to the blocks.

@@

Bipolar facial electromyography (EMG) will be measured for \emph{corrugator supercilii} and \emph{levator labii} as indices of affective valence\textsuperscript{60}, similar to previous work by our group\textsuperscript{7}.
Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of.\textsuperscript{61}
The ground electrode will be placed over the left \emph{Mastoid}.
Before electrode placement, the skin will be abraded with Every abrasive paste, cleaned with alcohol, and filled with Lectron III electrolyte gel.
Raw signals will be amplified by a BrainAmp amplifier (Brain Products Inc., Gilching, Germany).
Impedance level will be kept below 10 \(k\Omega\).
Data will be sampled at 1000 Hz, filtered, rectified and integrated.
A 20 Hz high pass (order 8), a 300 Hz low pass (order 8), and a 50 Hz notch filter will be applied to both signals.
Corrugator and Levator EMG will be analyzed during the 6 s of picture presentation.
EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset.\textsuperscript{60}
Last, the sampling rate will be changed to 100 Hz, and EMG data will be averaged for each condition and each participant.

@@

Sample size calculation is done using \emph{G*Power}\textsuperscript{62,63}.
In a meta-analysis of Zaehringer and colleagues\textsuperscript{5}, effect sizes of ER on peripheral-physiological measures were reported:
To find an effect of \(d=-0.32\) of ER on \emph{corrugator} muscle activity with \(\alpha=.05\) and \(\beta=.95\), data of at least \(N=85\) have to be analyzed.
Power analyses of all other hypotheses yielded smaller sample sizes.
However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
Therefore, we aim to collect data of \(N=120\) participants, about \(50%
\) more data sets, than necessary.
Detailed information on power calculation for each hypothesis can be found in the \protect\hyperlink{DesignTable}{design table}.

@@

Data collection and analysis will not be performed blind to the conditions of the experiments.
Data of whole participants will be excluded from analysis if participants withdraw their consent or they state that they did not follow experimental instructions.
EMG data of subjects will be excluded from analysis if errors occured during recording.
No further data exclusions are planned.
The level of significance will be set to \(\alpha=.05\).
For hypotheses H1-4, repeated measures analysis of variance (rmANOVA) will be conducted and estimated marginal means will be computed using the \emph{afex} package\textsuperscript{36}.
Greenhouse-Geisser-corrected degrees of freedom and associated \(p\)-values and will be reported when the assumption of sphericity is violated.
If the within-subjects factor of interest is significant, pairwise contrasts will be calculated using Bonferroni adjustment for multiple testing.
Proportion of explained variance \(\eta_{p}^{2}\) will be reported as a measure of effect size.

@@

\emph{Effects of emotion regulation on arousal, facial EMG and effort.}
To investigate the effects of the three ER strategies on subjective arousal (H2a), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective arousal ratings will be conducted.
To examine the effects of the three ER strategies on physiological responding (H3a and H3b), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for EMG \emph{corrugator} and \emph{levator} activity will be conducted.
To examine the effect of ER strategies on subjective effort (H4a), a rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings will be conducted.

@@

To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package\textsuperscript{64}.
First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
Restricted maximum likelihood (REML) will be applied to fit the model.
A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), and physiological responses (\emph{corrugator} and \emph{levator} activity) as level-1-predictors will be specified.
\[
SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + \text{utility} + corrugator \text{ activity} + levator \text{ activity} + (strategy|subject)
\]
Level-1-predictors will be centered within cluster\textsuperscript{65}.
Residuals of the final model will be inspected visually.
Intraclass correlation coefficient (ICC), \(\rho\), will be reported for each model (null model, as well as full model).

@@

For each result of the analyses, both \(p\)-values and Bayes factors \(BF10\), calculated using the \emph{BayesFactor} package\textsuperscript{37}, will be reported.
Bayes factors are calculated using the default prior widths of the functions \emph{anovaBF}, \emph{lmBF} and \emph{regressionBF}.

@@

\leavevmode\hypertarget{ref-Zerna2022}{}%
\CSLLeftMargin{31. }
\CSLRightInline{Zerna, J., Scheffel, C., Kührt, C. \& Strobel, A. When easy is not preferred: An effort discounting for estimating subjective values of taks. \emph{PsyArXiv} (2022) doi:\href{https://doi.org/10.31234/osf.io/ysh3q}{10.31234/osf.io/ysh3q}.}

\leavevmode\hypertarget{ref-Simmons2012}{}%
\CSLLeftMargin{32. }
\CSLRightInline{Simmons, J. P., Nelson, L. D. \& Simonsohn, U. A. A 21 word solution. \emph{SSRN Electronic Journal} (2012) doi:\href{https://doi.org/10.2139/ssrn.2160588}{10.2139/ssrn.2160588}.}

\leavevmode\hypertarget{ref-Peirce2019}{}%
\CSLLeftMargin{33. }
\CSLRightInline{Peirce, J. \emph{et al.} {PsychoPy2}: {Experiments} in behavior made easy. \emph{Behavior Research Methods} \textbf{51}, 195--203 (2019).}

\leavevmode\hypertarget{ref-RCore2021}{}%
\CSLLeftMargin{34. }
\CSLRightInline{R Core Team. \emph{R: A language and environment for statistical computing}. (R Foundation for Statistical Computing, 2021).}

\leavevmode\hypertarget{ref-RStudioTeam2020}{}%
\CSLLeftMargin{35. }
\CSLRightInline{RStudio Team. {RStudio}: {Integrated} development for {R}. (2020).}

\leavevmode\hypertarget{ref-Singmann2021}{}%
\CSLLeftMargin{36. }
\CSLRightInline{Singmann, H., Bolker, B., Westfall, J., Aust, F. \& Ben-Shachar, M. S. \emph{Afex: {A}nalysis of factorial experiments}. (2021).}

\leavevmode\hypertarget{ref-Morey2021}{}%
\CSLLeftMargin{37. }
\CSLRightInline{Morey, R. D. \& Rouder, J. N. \emph{{BayesFactor}: {Computation} of {Bayes} factors for common designs}. (2021).}

\leavevmode\hypertarget{ref-Greiner2015}{}%
\CSLLeftMargin{38. }
\CSLRightInline{Greiner, B. Subject pool recruitment procedures: {Organizing} experiments with {ORSEE}. \emph{Journal of the Economic Science Association} \textbf{1}, 114--125 (2015).}

\leavevmode\hypertarget{ref-Harris2009}{}%
\CSLLeftMargin{39. }
\CSLRightInline{Harris, P. A. \emph{et al.} Research electronic data capture ({REDCap})---{A} metadata-driven methodology and workflow process for providing translational research informatics support. \emph{Journal of Biomedical Informatics} \textbf{42}, 377--381 (2009).}

\leavevmode\hypertarget{ref-Harris2019}{}%
\CSLLeftMargin{40. }
\CSLRightInline{Harris, P. A. \emph{et al.} The {REDCap} consortium: {Building} an international community of software platform partners. \emph{Journal of Biomedical Informatics} \textbf{95}, 103208 (2019).}

>>>>

In the original study by Westbrook et al.\textsuperscript{29}, cognitive load was varied using the \emph{n}-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
Participants had to decide in an iterative procedure whether they wanted to repeat a higher \emph{n}-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption that the objectively easiest \emph{n}-back level has the highest SV.
In the present study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest \emph{n}-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies\textsuperscript{22}.
Moreover, there is nothing like an objectively easiest ER strategy.
It could be assumed, that the antecedent-focused strategies, i.e.~attentional deployment and cognitive change, require less effort, because according to Gross\textsuperscript{1} these strategies apply when the emotional reaction has not fully developed, yet.
In contrast, suppression would need ongoing effort, because it takes effect late in the emotion generating process and does not alter the emotion itself.
A similar assumption has been made by Mesmer-Magnus et al.\textsuperscript{31}, who state that Surface Acting (the equivalent to expressive suppression in emotional labor research) is supposed to continuously require high levels of energy (hence effort).
Deep Acting (which refers to reappraisal), in turn, only initially needs the use of energy.
This would be in conflict with findings in our previous studies, that showed that many people choose expressive suppression because they evaluated it as less effortful, hence easy\textsuperscript{22}.
Others define emotion regulation on a continuum from explicit, conscious, and effortful to implicit, unconscious, automatic and effortless\textsuperscript{32}.
This would mean, that all explicit strategies that have been proposed by the process model of emotion regulation are similarly effortful\textsuperscript{1}.
Similarly, the flexibility approach of emotion regulation also states, that there is no ``best'' strategy\textsuperscript{33}.
An emotion regulation attempt is adaptive, when the intended, individual goal is reached. Those attempts could also consist of sequences of regulatory efforts using different strategies, which might be effective and effortless only in this specific context.
Therefore, we have to add an additional step, which precedes the other steps and where the ER option with the higher subjective value is determined.
In this step, the same monetary value (i.e., 1 €) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al.\textsuperscript{29} until the indifference point is reached.
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \ref{fig:ResponsePatterns}).
In a separate study, we will test our adapted paradigm together with a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna et al.\textsuperscript{34}).

@@

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study\textsuperscript{35}.
The paradigm was written and presented using \emph{PsychoPy}\textsuperscript{36}.
We used \emph{R} with \emph{R Studio}\textsuperscript{37,38} with the main packages \emph{afex}\textsuperscript{39} and \emph{BayesFactor}\textsuperscript{40} for all analyses.
The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at \url{https://github.com/ChScheffel/CERED}.
A complete list of all measures assessed in the study can be found at OSF (\url{https://osf.io/vnj8x/}) and GitHub (\url{https://github.com/ChScheffel/CERED}).

@@

Young healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{41} at the Technische Universität Dresden.
Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
Participants will be invited to complete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consists of two lab sessions, which will take place in a shielded cabin with constant lighting.
Before each session, participants will receive information about the respective experimental procedure and provide informed consent.
In the first session participants will fill out a demographic questionnaire and complete an n-back task with the levels one to four.
Then, they will complete an effort discounting (ED) procedure regarding the n-back levels on screen, followed by a random repetition of one n-back level.
The second session will take place exactly one week after session one.
Participants will provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
A brief training will ensure that all participants are able to implement the ER strategies.
Next, electrodes to measure facial EMG will be attached and the ER paradigm will be conducted, followed by an ED procedure regarding the ER strategies.
After that, participants will choose one ER strategy to repeat one more time.
Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden\textsuperscript{42,43}.

@@

The online survey will contain a number of questionnaires.
In the focus of the current project is the Flexible Emotion Regulation Scale (FlexER)\textsuperscript{44}.\\
It assess flexible use of ER strategies with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which we define as ER flexibility.
The items are rated on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.

Further psychological constructs will be assessed but have no clear hypothesies in the present work an are therefore investigated only exploratory:
General psychological well-being will be assessed using the German version of the WHO-5 scale\textsuperscript{45,46}.
To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{49} will be used.
Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from Bernecker and Job\textsuperscript{51}.
To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{28,52} will be used.
To assess self-control,\textsuperscript{53} sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS)\textsuperscript{54}, the Brief Self-Control Scale (BSCS)\textsuperscript{55,56}, and the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{57,58}.
Attentional control will be assessed using the Attentional Control Scale (ACS)\textsuperscript{59}.
For more detailed information on psychometric properties of the questionnaires, please see \protect\hyperlink{SupplementQuestionnaires}{supplementary material}.

@@

\emph{Part one: ER task.} Part one will be a standard ER task in a block design (see Figure \ref{fig:DesignERED}), similar to paradigms previously used by our group\textsuperscript{22}.
Participants will be told to actively view neutral and negative pictures (see \protect\hyperlink{ux5cux23stimuli}{2.3.3}) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
Every participant first will have the condition ``active viewing-neutral'' that serves as a baseline condition.
During this block, 20 neutral pictures will be presented.
Participants will be asked to ``actively view all pictures and permit all emotions that may arise.''
In the second block, participants will actively view negative pictures.
During the third, fourth, and fifth block, participants will see negative pictures and will be asked to regulate their emotions using distraction, distancing, and suppression.
In order to achieve distraction, participants will be asked to think of a geometric object or an everyday activity, like brushing their teeth.
During distancing, participants will be asked to ``take the position of a non-involved observer, thinking about the picture in a neutral way.''
Participants will be told not to re-interpret the situation or attaching a different meaning to the situation.
During suppression, participants will be told to ``suppress their emotional facial expression.''
They should imagine being observed by a third person that should not be able to tell by looking at the facial expression whether the person is looking at an emotional picture.
Participants will be instructed not to suppress their thoughts or change their facial expression to the opposite\textsuperscript{22}.
All participants will receive written instruction and complete a training session.
After the training session, participants will be asked about their applied ER strategies to avoid misapplication.
The order of the three regulation blocks (distraction, distancing, and suppression) will be randomized between participants.
Each of the blocks consists of 20 trials showing neutral (Block 1) and negative (Blocks 2, 3, 4, 5) pictures.
Each trial begins with a fixation cross that lasts 3 to 5 seconds (random uniform distributed).
It is followed by neutral or negative pictures for a total of 6 seconds.
After each block, participants retrospectively will rate their subjective emotional arousal (``not at all aroused'' to ``very highly aroused''), their subjective effort (``not very exhausting'' to ``very exhausting''), and - after the ragulation blocks - the utility of the respective strategy (``not useful at all'' to ``very useful'') on a continuous scale using a slider on screen.

@@

Pictures that will be used in the paradigm are selected from the Emotional Picture Set (EmoPicS)\textsuperscript{60} and the International Affective Picture System (IAPS)\textsuperscript{61}.
The 20 neutral pictures (Valence (V): \emph{M} \(\pm\) \emph{SD} = 4.81 \(\pm\) 0.51; Arousal (A): \emph{M} \(\pm\) \emph{SD} = 3 \(\pm\) 0.65) depicted content related to the categories persons, objects, and scenes.
Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, will be used.
An evolutionary algorithm\textsuperscript{62} is used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
A complete list of all pictures and their classification into sets can be found in supplementary material 1.
The five sets of negative pictures will be assigned randomly to the blocks.

@@

Bipolar facial electromyography (EMG) will be measured for \emph{corrugator supercilii} and \emph{levator labii} as indices of affective valence\textsuperscript{63}, similar to previous work by our group\textsuperscript{7}.
Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of.\textsuperscript{64}
The ground electrode will be placed over the left \emph{Mastoid}.
Before electrode placement, the skin will be abraded with Every abrasive paste, cleaned with alcohol, and filled with Lectron III electrolyte gel.
Raw signals will be amplified by a BrainAmp amplifier (Brain Products Inc., Gilching, Germany).
Impedance level will be kept below 10 \(k\Omega\).
Data will be sampled at 1000 Hz, filtered, rectified and integrated.
A 20 Hz high pass (order 8), a 300 Hz low pass (order 8), and a 50 Hz notch filter will be applied to both signals.
Corrugator and Levator EMG will be analyzed during the 6 s of picture presentation.
EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset.\textsuperscript{63}
Last, the sampling rate will be changed to 100 Hz, and EMG data will be averaged for each condition and each participant.

@@

Sample size calculation is done using \emph{G*Power}\textsuperscript{65,66}.
In a meta-analysis of Zaehringer and colleagues\textsuperscript{5}, effect sizes of ER on peripheral-physiological measures were reported:
To find an effect of \(d=-0.32\) of ER on \emph{corrugator} muscle activity with \(\alpha=.05\) and \(\beta=.95\), data of at least \(N=85\) have to be analyzed.
Power analyses of all other hypotheses yielded smaller sample sizes.
However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
Therefore, we aim to collect data of \(N=120\) participants, about \(50%
\) more data sets, than necessary.
Detailed information on power calculation for each hypothesis can be found in the \protect\hyperlink{DesignTable}{design table}.

@@

Data collection and analysis will not be performed blind to the conditions of the experiments.
Data of whole participants will be excluded from analysis if participants withdraw their consent or they state that they did not follow experimental instructions.
EMG data of subjects will be excluded from analysis if errors occured during recording.
No further data exclusions are planned.
The level of significance will be set to \(\alpha=.05\).
For hypotheses H1-4, repeated measures analysis of variance (rmANOVA) will be conducted and estimated marginal means will be computed using the \emph{afex} package\textsuperscript{39}.
Greenhouse-Geisser-corrected degrees of freedom and associated \(p\)-values and will be reported when the assumption of sphericity is violated.
If the within-subjects factor of interest is significant, pairwise contrasts will be calculated using Bonferroni adjustment for multiple testing.
Proportion of explained variance \(\eta_{p}^{2}\) will be reported as a measure of effect size.

@@

\emph{Effects of emotion regulation on arousal, facial EMG and effort.}
To investigate the effects of the three ER strategies on subjective arousal (H2a), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective arousal ratings will be conducted.
To examine the effects of the three ER strategies on physiological responding (H3a and H3b), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for EMG \emph{corrugator} and \emph{levator} activity will be conducted.
To examine the effect of ER strategies on subjective effort (H4a), a rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective effort ratings will be conducted.

@@

To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package\textsuperscript{67}.
First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
Restricted maximum likelihood (REML) will be applied to fit the model.
A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), and physiological responses (\emph{corrugator} and \emph{levator} activity) as level-1-predictors will be specified.
\[
SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + \text{utility} + corrugator \text{ activity} + levator \text{ activity} + (strategy|subject)
\]
Level-1-predictors will be centered within cluster\textsuperscript{68}.
Residuals of the final model will be inspected visually.
Intraclass correlation coefficient (ICC), \(\rho\), will be reported for each model (null model, as well as full model).

@@

For each result of the analyses, both \(p\)-values and Bayes factors \(BF10\), calculated using the \emph{BayesFactor} package\textsuperscript{40}, will be reported.
Bayes factors are calculated using the default prior widths of the functions \emph{anovaBF}, \emph{lmBF} and \emph{regressionBF}.

@@

\leavevmode\hypertarget{ref-MesmerMagnus2012}{}%
\CSLLeftMargin{31. }
\CSLRightInline{Mesmer-Magnus, J. R., DeChurch, L. A. \& Wax, A. Moving emotional labor beyond surface and deep acting: A discordance-congruence perspective. \emph{Organizational Psychology Review} \textbf{2}, 6--53 (2012).}

\leavevmode\hypertarget{ref-Gyurak2011}{}%
\CSLLeftMargin{32. }
\CSLRightInline{Gyurak, A., Gross, J. J. \& Etkin, A. Explicit and implicit emotion regulation: A dual-process framework. \emph{Cogn Emot} \textbf{25}, 400--12 (2011).}

\leavevmode\hypertarget{ref-Gross2015}{}%
\CSLLeftMargin{33. }
\CSLRightInline{Gross, J. J. Emotion regulation: Current status and future prospects. \emph{Psychological Inquiry} \textbf{26}, 1--26 (2015).}

\leavevmode\hypertarget{ref-Zerna2022}{}%
\CSLLeftMargin{34. }
\CSLRightInline{Zerna, J., Scheffel, C., Kührt, C. \& Strobel, A. When easy is not preferred: An effort discounting for estimating subjective values of taks. \emph{PsyArXiv} (2022) doi:\href{https://doi.org/10.31234/osf.io/ysh3q}{10.31234/osf.io/ysh3q}.}

\leavevmode\hypertarget{ref-Simmons2012}{}%
\CSLLeftMargin{35. }
\CSLRightInline{Simmons, J. P., Nelson, L. D. \& Simonsohn, U. A. A 21 word solution. \emph{SSRN Electronic Journal} (2012) doi:\href{https://doi.org/10.2139/ssrn.2160588}{10.2139/ssrn.2160588}.}

\leavevmode\hypertarget{ref-Peirce2019}{}%
\CSLLeftMargin{36. }
\CSLRightInline{Peirce, J. \emph{et al.} {PsychoPy2}: {Experiments} in behavior made easy. \emph{Behavior Research Methods} \textbf{51}, 195--203 (2019).}

\leavevmode\hypertarget{ref-RCore2021}{}%
\CSLLeftMargin{37. }
\CSLRightInline{R Core Team. \emph{R: A language and environment for statistical computing}. (R Foundation for Statistical Computing, 2021).}

\leavevmode\hypertarget{ref-RStudioTeam2020}{}%
\CSLLeftMargin{38. }
\CSLRightInline{RStudio Team. {RStudio}: {Integrated} development for {R}. (2020).}

\leavevmode\hypertarget{ref-Singmann2021}{}%
\CSLLeftMargin{39. }
\CSLRightInline{Singmann, H., Bolker, B., Westfall, J., Aust, F. \& Ben-Shachar, M. S. \emph{Afex: {A}nalysis of factorial experiments}. (2021).}

\leavevmode\hypertarget{ref-Morey2021}{}%
\CSLLeftMargin{40. }
\CSLRightInline{Morey, R. D. \& Rouder, J. N. \emph{{BayesFactor}: {Computation} of {Bayes} factors for common designs}. (2021).}
